---
title: "HW6_interactivity"
author: "Manali Phadke, Muhire Kwizera"
date: "November 13, 2017"
output: html_document
---

```{r, message=FALSE}
#loaded packages 
library(tidyverse)
library(dplyr)
library(plotly)
library(janitor)
library(forcats)

instacart_data = read_csv("./data/instacart_train_data.csv.zip") %>%
  clean_names()
```
The number of observations in the instacart dataset is `r nrow(instacart_data)`
The number of variables in the instacart dataset is `r ncol(instacart_data)`


These are descriptions of the relavent variables:
  department: the name of the department
  
  product_name: the name of the product
  
  order_hour_of_day:hour of day when the order was placed
  
  reordered: whether the product was reordered or not.
  
##Make histogram of order hour of day for personal care department
```{r}
instacart_data %>% 
  filter(department == "personal care") %>% 
  plot_ly(x = ~order_hour_of_day, type = "histogram", color = "red") %>% 
  layout(yaxis = list(title = "count"))
```

##Make a barplot of number of orders for each department
```{r}
instacart_data %>%
  mutate(department = factor(department)) %>%
  group_by(department) %>%
    summarize(num_orders = n()) %>%
    mutate(department = fct_reorder(department, -num_orders)) %>% 
    plot_ly(x = ~department, y = ~num_orders, type = "bar", color = ~department) %>%
    layout(margin = list(l = 50, r = 10, t = 15, b = 140))


```


```{r}
instacart_data_orders = instacart_data %>%
  group_by(product_name, department) %>%
  summarize(num_order = n())
  
  
instacart_data_reorders = instacart_data %>%
  filter(reordered == 1) %>%
  # select(reordered, product_name, department) %>%
  group_by(product_name) %>%
  summarize(num_reorder = n())
  
instacart_data_order_reorder = left_join(instacart_data_orders, instacart_data_reorders, by = "product_name") %>%
  replace_na(list(num_reorder = 0))

# Plotly scatter plot
instacart_data_order_reorder %>% 
plot_ly(x = ~num_order, y = ~num_reorder, type = "scatter", color = ~department)
```


